---
title: "Answer Key"
author: "Don Z"
date: '2022-07-21'
output:
  pdf_document: 
    toc: yes
    toc_depth: 2
    number_sections: yes
  html_document:
    toc: yes
    toc_depth: '2'
    df_print: paged
---

# General Instructions

Below you will find a list of tasks. Some tasks require you to provide a answer. In this case, please type your answer directly under the question and format your answer in **bold**. In other cases, you may be asked to write some code in a blank code chunk. 

Some of the tasks will require you to pull code from the analysisTemplate repo. Find it here: https://github.com/dczhang1/analysisTemplates.git

## 1. Please change the title, author, and date of this rmd file to something reasonable

## 2. Run the following code chunk and explain what the purpose of this code chunk in a sentence or two.

```{r}
source("01_load.R")
```

## 2. Write the script to import the dataset in the code chunk below. Name the dataframe as "df_risk_raw". Also explain words, where would this code go in a normal project? In other words, if not working on this worksheet, where would the code for importing data go? 

```{r import data}




```

## 3. Run the code above to make sure that the data is imported with no errors and is shown in your Enviornment

## 4. Look at the data object df_risk_raw. How many subjects and variables are in this dataframe? 

## 5. Run the following chunk to see a list of variables
```{r}
names(df_risk_raw)
```

## 6. Find the "Reference" folder in the file directory and open the codebook word document to answer the following questions:

### 6.1) What is variable HH6?

### 6.2) What is variable CW15?

### 6.3) Which items are part of the "Genearl Risk Propensity Scale"?

### 6.4) How many items are in the Perceived Disadvantage Index?

## 7. Write the script for creating a dataframe that contains *only* the items for the General Risk Propensity Scale

```{r}




```

## 8. Write the script for creating a dataframe with participants between ages 18 and 24

```{r}




```

## 9. Create a new variable in the data frame "Mean_GRIPS" based on the average of all of the items in the General Risk Propensity Scale using the rowMeans function (find script in the 02_clean.R file in the analysisTemplate repo)

```{r}





```

## 10. Repeat step 9 using the **scoreItem** function provided in the same file. For this situation, all the items are positively coded. Name this new variable "Mean_GRIPS_2"

```{r}




```

We will now perform some very basic descriptive statistics on our dataset.

## 11. We will first calculate the mean, standard deviation, and variance of the Mean_GRIPS variable. Just run the following script. 

```{r}




```

## 12. Now use the **describe** function on the Mean_GRIPS variable to create a more thorough summary

```{r}





```

## 13. Create a histogram of the variable Mean_GRIPS (hint: See script in 3_describe.R)

```{r}
   



```

## 14. Create a frequency table of education attainment within the sample

```{r}




```

## 15. Create a subset of the dataframe with variables: Age, Gender, and the Mean_GRIPS variable

```{r}





```

#16. We will make a simple correlation table using the apa.cor.table function in the package apaTables. First, type ?apa.cor.table into the console for a brief documentation.

#17. Now, make a correlation table with Age, Gender, and Mean_GRIPS. (Find this script in the 3_descriptive.R from the template.)

```{r}




```

#18. Produce descriptive statistics for Age, Gender, and Mean_GRIPS using the **describe** function (hint: you should be able to do this in one line of code)

```{r}




```

Your done! Now, go back to the top and make sure every chunk still works. Press the "Knit to HTML" button to turn all of this into a html document. If there are errors, please review the error message. Send the output HTML file to Don. 

#19. Bonus: Make your HTML pretty with the prettydoc package: https://prettydoc.statr.me/ Follow instructions here to produce a beautified version of the document. 

**Final remarks**: we will be using rmarkdown notebooks like this for sharing reports/results. You may perform your analysis in rmd notebooks like for your own work. However, you may use R Script files to keep your actual code, if you wish. 